opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-22 chapters/00_abstract.tex
Added paragraph by Hodge group

Powder X-ray diffraction (pXRD) experiments are a cornerstone for materials structure characterization.
Despite their widespread application, the analysis of pXRD diffractograms still presents a significant challenge to automation and thus a bottleneck in high-throughput experimentation of automated materials discovery in self-driving labs.
Machine learning has emerged as a promising research direction to resolve this bottleneck by enabling automated powder diffraction data analysis.
A notable difficulty in applying machine learning to this domain is the lack of sufficiently sized experimental datasets, which has relegated machine learning researchers to train primarily on simulated data. Since simulations largely fail to accurately reflect the experiment, the performance of models trained on only simulated data often lacks transferability to experimental data and thus currently falls short of providing value in practice.
With the Open Experimental Powder X-Ray Diffraction Database (opXRD), we aim to remedy this by providing an openly available and easily accessible dataset of both labeled and unlabeled experimental powder diffractograms, providing machine learning researchers with a large quantity of real experimental diffractograms collected from a broad range of samples. The labeled data can be used as a benchmark to evaluate the performance of models on real experimental data and unlabeled data can help improve the performance of models on experimental data through transfer learning methods. 
%We provide almost barrier-free software tools that allow experimental researchers to find their data and make it accessible - in virtually any widely used format.
We collected XXX labeled and YYY unlabeled diffractograms from a wide spectrum of materials classes, which establishes the first version of the opXRD database.
We hope that this ongoing effort can guide machine learning research toward fully automated analysis of pXRD data and thus enable future self-driving materials labs.

>>>>

Powder X-ray diffraction (pXRD) experiments are a cornerstone for materials structure characterization.
Despite their widespread application, the analysis of pXRD diffractograms still presents a significant challenge to automation and thus a bottleneck in high-throughput experimentation of automated materials discovery in self-driving labs.
Machine learning has emerged as a promising research direction to resolve this bottleneck by enabling automated powder diffraction data analysis.
A notable difficulty in applying machine learning to this domain is the lack of sufficiently sized experimental datasets, which has relegated machine learning researchers to train primarily on simulated data. However, models trained on simulated pXRD patterns showed limited generalization ability when applied to experimental patterns, particularly with low-quality experimental pattern that has high noise levels and elevated background.
%Therefore, developing an experimental database offers at least two key advantages: (1) providing a comprehensive benchmark dataset to clarify model performance in practical applications, and (2) advancing phase identification tasks by supplying target-domain data within a transfer learning framework.
With the Open Experimental Powder X-Ray Diffraction Database (opXRD), we aim to provide an openly available and easily accessible dataset of both labeled and unlabeled experimental powder diffractograms, providing machine learning researchers with a large quantity of real experimental diffractograms collected from a broad range of samples. The labeled data can be used as a benchmark to evaluate the performance of models on real experimental data and unlabeled data can help improve the performance of models on experimental data through transfer learning methods. 
%We provide almost barrier-free software tools that allow experimental researchers to find their data and make it accessible - in virtually any widely used format.
We collected XXX labeled and YYY unlabeled diffractograms from a wide spectrum of materials classes, which establishes the first version of the opXRD database.
We hope that this ongoing effort can guide machine learning research toward fully automated analysis of pXRD data and thus enable future self-driving materials labs.

### 2024-11-22 chapters/01_introduction.tex
Added paragraph by Hodge group

% On Rietveld refinement
After fabricating a new material, a number of analysis techniques can be used to characterize the sample. One method that can be used to determine the crystal structure of a new material is powder X-ray diffraction. To determine crystal structure from pXRD data, an initial guess is optimized using Rietveld refinement. In this process, an initial crystal structure including unit cell parameters is provided by the operator of the analysis software and fitted to the observed diffractogram in an iterative optimization process based on simulated forward prediction of expected pXRD diffractograms given the current crystal structure. \cite{Dinnebier2019, Cano2021} As Rietveld refinement is a local optimization method, the result of the refinement procedure is only as good as the initial guess it was provided with. \\

@@

At the moment, the number of openly available datasets for experimental powder data is very limited. The main sources for experimental patterns are XXX, YYY, and ZZZ. Further commercial datasets such as KKK and LLL exist, but license fees and restrictions in their use to train publishable models or even publish the training data limit their usability. Collecting a labeled dataset of raw experimental powder X-ray diffraction data of sufficient size to directly train a model that predicts crystal structure information is likely out of reach. The most advanced ML models currently are trained on approximately $10^7 - 10^8$ simulated diffractograms, which is - to the best of our knowledge - three orders of magnitude larger than the largest currently curated experimental dataset and even x orders of magnitude larger than the number of unlabeled diffractograms in the opXRD dataset we present here. \\

@@

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality.
One can bring the simulated patterns closer to experiment by improving the simulation itself by properly modeling more of the observed physical effects such as preferred orientation, peak shapes resulting from different sources, etc.
Additionally, some of the observed imperfections, such as background and noise, can be modeled using machine learning approaches. This is similar to the concept of style transfer\cite{Gatys2016, Ganin2015} found in the domain of machine learning applied to images. Here, the objective is to obtain a classification or regression model when only labeled images of one style (simulated data) and unlabeled or partially labeled images of another style (experimental data) are available. \\

In this publication, we provide a new open powder X-ray diffraction (opXRD) dataset that collects a broad range of patterns from experiment, exceeding the currently available amount of openly accessible experimental patterns by XX.
Our opXRD dataset has been curated by collecting the accumulated powder data from multiple large research groups and institutions with high-throughput XRD facilities. It contains pXRD patterns from single and multiphase materials from a wide variety of materials classes, including XXX, YYY, and ZZZ. Details about the experiments of contributing research groups are discussed in this paper, along with a detailed description of how to contribute further data and how to use the data. \\

@@

>>>>

% On Rietveld refinement
After fabricating a new material, a number of analysis techniques can be used to characterize the sample. One method that can be used for phase identification, phase quantification, grain size characterization, and partially to determine the crystal structure of a new material is powder X-ray diffraction. To determine crystal structure from pXRD data, an initial guess is optimized using Rietveld refinement. In this process, an initial crystal structure including unit cell parameters is provided by the operator of the analysis software and fitted to the observed diffractogram in an iterative optimization process based on simulated forward prediction of expected pXRD diffractograms given the current crystal structure. \cite{Dinnebier2019, Cano2021} As Rietveld refinement is a local optimization method, the result of the refinement procedure is only as good as the initial guess it was provided with. \\

@@

At the moment, the number of openly available datasets for experimental powder data is very limited. The main sources for experimental patterns are XXX, YYY, and ZZZ. Further commercial datasets such as KKK and LLL exist, but license fees and restrictions in their use to train publishable models or even publish the training data limit their usability. Collecting a labeled dataset of raw experimental powder X-ray diffraction data of sufficient size to directly train a model that predicts crystal structure information is likely out of reach. The most advanced ML models currently are trained on approximately $10^7 - 10^8$ simulated diffractograms, which is - to the best of our knowledge - three orders of magnitude larger than the largest currently curated experimental dataset (PDF-5+ with approximately 20,000 experimental patterns) and even x orders of magnitude larger than the number of unlabeled diffractograms in the opXRD dataset we present here. \\

@@

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality.
One can bring the simulated patterns closer to experiment by improving the simulation itself by properly modeling more of the observed physical effects such as preferred orientation, peak shapes resulting from different sources, etc.
Additionally, some of the observed imperfections, such as background and noise, can be modeled using machine-learning approaches. This is similar to the concept of style transfer\cite{Gatys2016, Ganin2015} found in the domain of machine learning applied to images. Here, the objective is to obtain a classification or regression model when only labeled images of one style (simulated data) and unlabeled or partially labeled images of another style (experimental data) are available. \\

In this publication, we provide a new open powder X-ray diffraction (opXRD) dataset that collects a broad range of patterns from experiments, exceeding the currently available amount of openly accessible experimental patterns by XX.
Our opXRD dataset has been curated by collecting the accumulated powder data from multiple large research groups and institutions with high-throughput XRD facilities. It contains pXRD patterns from single and multiphase materials from a wide variety of materials classes, including XXX, YYY, and ZZZ. Details about the experiments of contributing research groups are discussed in this paper, along with a detailed description of how to contribute further data and how to use the data. \\

@@

% TODOS: These papers talk about the importance of sharing raw diffraction data/ raw powder diffraction data them
%  1 | \cite{Aranda2018}
% 2 | Raw diffraction data and reproducibility

### 2024-11-22 chapters/02_existing_datasets.tex
Added paragraph by Hodge group

% Sources to mention
% Zenodo -> A good amount of raw powder data there but spread into smaller datasets; Inhomogenous, not specially prepared to be worked with by others, therefore difficult to work with especially at scale

% Crystal structures with corresponding simulated diffractograms;
% ->  ICSD 
% - 230k structures;
% - Proprietary

% -> PDF  -> 
%- 1200k "material data sets" (structures?) 
% + 19 k entries with "Experimental raw data digital patterns"; 
%  Proprietary (% PDF pricing: https://www.icdd.com/assets/files/2023-Purchase-Options.pdf)
%The PDF itself lists the following data sources:

% ->  COD (https://www.crystallography.net/cod/)
% -  513k structures,
% - Fully open

% Datset listing (Done on: 20.06.24)
% I would list here *all* crystallography databases but evaluate/determine that they lack or don't provide convenient access to raw powder diffraction data

% Some other Lists of Crystallographic databases
% - IUCR: "Crystallographyic databases and related resources" (https://www.iucr.org/resources/data/databases)
% - Bruno et al. (2017): "Crystallography and Databases" (https://datascience.codata.org/articles/10.5334/dsj-2017-038)
% - University of Virginia "Crystallographic data" (https://guides.lib.virginia.edu/c.php?g=514782&p=3568808)

%->1 PDF5+ (https://www.icdd.com/,https://www.icdd.com/pdf-5/)
% - Data sources of the PDF
% (1.1): ICDD Powders
% (1.2): FIZ ICSD (https://icsd.products.fiz-karlsruhe.de/)
% (1.3): NIST ICSD https://icsd.nist.gov/
% (1.4): Linus Pauling File (https://paulingfile.com/index.php?p=about%20us)
% (1.5): ICDD Single Crystal data
%-> 2 COD (https://www.crystallography.net/cod/)
%-> 3 RRUFF (American Mineralogist Crystal Structure Database)
%-> 4 CCDC (https://www.ccdc.cam.ac.uk/)
%-> 5 The Material Project (https://legacy.materialsproject.org/)
%-> 6 Crystal Lattice Structures (https://www.atomic-scale-physics.de/lattice/)
%-> 7 Crystallographic and Crystallochemical Database for Minerals and their Structural Analogues (https://database.iem.ac.ru/mincryst/)
%-> 8 Mineralogy Database (https://webmineral.com/)
%-> 9 IUCr Raw data letters (https://iucrdata.iucr.org/)
%-> 10 Bilbao Crystallographic server  (https://www.cryst.ehu.es/)
%-> 11 PowBase (http://www.cristal.org/powbase/index.html)
%-> 12 Athena (https://athena.unige.ch/athena/mineral/mineral.html)
%-> 13 Protein database (https://www.rcsb.org/)
%-> 14 SDPD (Structure Determination from Powder Diffraction - Database)
%-> 15 Crystal Met (https://cds.dl.ac.uk/cds/datasets/crys/mdf/llmdf.html)
%-> 16 NAKB (https://www.nakb.org/)
%-> 17 Pearson's Crystal data (https://www.crystalimpact.com/pcd/)
%-> 18 Biological macromolecule Crystallization Database (http://bmcd.ibbr.umd.edu/)

%TODO: Also include plans for NOMAD and highlight their efforts

@@

\paragraph{Existing powder diffraction datasets} To contextualize opXRD within the current environment of experimental powder diffraction data, the following list provides an overview of the largest crystal structure databases that include powder diffraction data.

@@

\item Scattered experimental datasets on Zenodo (TODO: roughly estimate size)
\item \textbf{RRUFF}: The RRUFF Mineral Database \cite{Armbruster2015} provides detailed information on minerals, including their chemical compositions, crystallography, and spectroscopic data. Managed by the University of Arizona, it was created to serve as a public repository for mineral identification and research. It contains \num{908} distinct structures with experimental x-ray diffraction patterns.
\item ...
\end{itemize}

>>>>

% Datset listing (List written on 20.06.24)
% Some other Lists of Crystallographic databases
% - IUCR: "Crystallographic databases and related resources" (https://www.iucr.org/resources/data/databases)
% - Bruno et al. (2017): "Crystallography and Databases" (https://datascience.codata.org/articles/10.5334/dsj-2017-038)
% - University of Virginia "Crystallographic data" (https://guides.lib.virginia.edu/c.php?g=514782&p=3568808)

% [X] 1 PDF5+ (https://www.icdd.com/,https://www.icdd.com/pdf-5/) -> 19000 structures with pXRD patterns | I checked with their support
    % (1.1): ICDD Powders
    % (1.2): FIZ ICSD (https://icsd.products.fiz-karlsruhe.de/)
    % (1.3): NIST ICSD https://icsd.nist.gov/
    % (1.4): Linus Pauling File (https://paulingfile.com/index.php?p=about%20us)
    % (1.5): ICDD Single Crystal data
% [x]: 2 COD (https://www.crystallography.net/cod/) -> ~ 1000 structures with real pXRD patterns | These patterns were extracted by PSL university
% [x]: 3 RRUFF (American Mineralogist Crystal Structure Database) -> ~ 1000 structures with real pXRD patterns | We downloaded the entire dataset and discarded single crystal data
% [x]: 4 CCDC (https://www.ccdc.cam.ac.uk/) -> No exp pXRD | There is only mention of simulated powder diffraction data. Of 20 sampled cifs none contained powder diffraction data
% [x]: 5 The Material Project (https://legacy.materialsproject.org/) -> No exp pXRD | The only mention of available X-ray diffraction data is of simulated data
% [x]: 6 Crystal Lattice Structures (https://www.atomic-scale-physics.de/lattice/) -> No exp pXRD | Their entries provide no X-ray diffraction data, and also most links appear broken
% [x]: 7 Crystallographic and Crystallochemical Database for Minerals and their Structural Analogues (https://database.iem.ac.ru/mincryst/) -> No exp pXRD | The given powder diffraction data is simulated (see: Powder X-ray Diffraction Standards (CPDS) @ https://database.iem.ac.ru/mincryst/descript.htm)
% [x]: 8 Mineralogy Database (https://webmineral.com/) -> No exp pXRD | I checked with the author of the site
% [x]: 9 IUCr Raw data letters (https://iucrdata.iucr.org/) -> No exp pXRD | There are only two raw data letters, both of them single crystal data
% [x]: 10 Bilbao Crystallographic server  (https://www.cryst.ehu.eus/bincstrdb/search/) No exp pXRD | Of 20 sampled CIFs out of 256 entries none contained pXRD data
% [x]: 11 PowBase (http://www.cristal.org/powbase/index.html) -> 169 real pXRD patterns some of which have at least partial labels; The described submission process and the lack of crystal structures indicate that the patterns are not simulated
% [x]: 12 Athena (https://athena.unige.ch/athena/mineral/mineral.html) -> No exp pXRD | No mention of diffraction data anywhere
% [x]: 13 Protein database (https://www.rcsb.org/) / NAKB (https://www.nakb.org/) / BMCD ((http://bmcd.ibbr.umd.edu/)  -> Little to no exp pXRD | Of the 230k structures only 21 showed up when searching experimental method = Powder diffraction
% [x]: 14 Crystal Met (https://cds.dl.ac.uk/cds/datasets/crys/mdf/llmdf.html) -> No exp pXRD | The only mention of diffraction data is simulated data
% [x]: 15 Pearson's Crystal data (https://www.crystalimpact.com/pcd/) -> 21700 experimental powder diffraction patterns (As per https://www.crystalimpact.com/pcd/) | The Pearson's crystal data evolved from the Linus Pauling File which is a data source of the PDF, so there may be significant overlap in these patterns
% [x]: 16 Zenodo powder diffraction data (https://zenodo.org/search?q=powder%20diffraction&l=list&p=1&s=10&sort=bestmatch) -> Some pXRD data but hard to quantify, probably <= 4000 patterns most of which are unlabeled | 1600 datasets matching "powder diffraction". From probing among the first 100 matches I estimate only about 1 in 10 contain powder diffraction patterns. The probed datasets that did contain powder diffraction data only contained <= 30 patterns and only one of them came with corresponding crystal structures

@@

\paragraph{Existing experimental powder diffraction datasets} To contextualize opXRD within the current environment of experimental powder diffraction data, the following list provides an overview of the largest crystal structure databases that include powder diffraction data.

@@

\item Scattered experimental datasets on Zenodo (TODO: roughly estimate size)

\item \textbf{RRUFF}: The RRUFF Mineral Database \cite{Armbruster2015} provides detailed information on minerals, including their chemical compositions, crystallography, and spectroscopic data. Managed by the University of Arizona, it was created to serve as a public repository for mineral identification and research. It contains \num{908} distinct structures with experimental x-ray diffraction patterns.

\end{itemize}

### 2024-11-22 chapters/03_SOTA_ML.tex
Added paragraph by Hodge group

@@

Using simulated diffractograms based on structures from the ICSD, Lee et al. managed to train a deep convolutional neural network (CNN) that is able to classify occurring phases in diffractograms of a specific compound pool. \cite{Lee2020} Building upon their work they also developed models based on fully convolutional neural networks and transformer encoders, that predict the crystal system and the spacegroup and other structural properties, such as the band gap \cite{Lee2022}. With their best model for the crystal system prediction on ICSD structures, they achieved a test accuracy of \SI{92.2}{\percent}.
Park et al. reached a test accuracy of roughly 81\% for a CNN, which classifies space groups of simulated single-phase diffractograms. \cite{Park2017}
A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi et al.\cite{Chitturi2021} They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles. Zhang and Cao et al.\cite{zhang2024crystallographic} introduce a convolutional self-attention neural network trained on simulated patterns to classify crystal types. Their model was tested on 23,073 unary, binary, and ternary inorganic crystal structures sourced from the Crystallography Open Database. The study observed a noticeable performance drop when the pretrained model was applied to real experimental patterns, as opposed to simulated data. However, their recent work \cite{cao2024simxrd} proposes using convolutional peak descriptors that consider the detector's geometry, which significantly reduces the performance gap in their benchmark tests.
The option of training purely on experimental diffractograms unfortunately is unfeasible because of the limited availability of labeled experimental diffractograms, but Salgado et al. \cite{Salgado2023} showed, that adding a fraction of experimental patterns to a simulated training dataset improves the performance on unseen experimental patterns. They used \SI{50}{\percent} of the experimental patterns contained in the RRUFF database and added those to their large simulated training set. Then they tested their model's performance on the other half of the RRUFF database and achieved a performance increase in the 230-way spacegroup classification accuracy of \num{11} percentage points compared to the same model only trained on simulated patterns.

@@

The ultimate goal of this ML technology is to make PXRD data identification practical for experimental use, whether for identifying space group symmetry or phase composition. However, the current volume of experimental PXRD patterns is insufficient to effectively train ML models, highlighting an urgent need for a comprehensive experimental PXRD database. To address this, two key approaches are essential. First, developing more sophisticated simulation methods to better approximate experimental patterns\cite{cao2024simxrd}. Second, creating an experimental database that enables transfer learning to bridge the gap between simulated and real-world data. The development of opXRD is particularly significant, as it will provide a comprehensive experimental benchmark for the community, allowing fair comparison of baseline models and accurate evaluation of their applicability in real experimental situations.

>>>>

%TODO:
% - Papers to include: https://pubs.acs.org/doi/10.1021/jacs.4c10244
% - Sagado et al.: Automated classification of big X-ray diffraction data using deep learning models

@@

Using simulated diffractograms based on structures from the ICSD, Lee {\it et al.} trained a deep convolutional neural network (CNN) that is able to classify occurring phases in diffractograms of a specific compound pool \cite{Lee2020}. They furthermore developed models based on fully convolutional neural networks and transformer encoders that predict the crystal system and the spacegroup and other structural properties, such as the band gap \cite{Lee2022}. With their best model for the crystal system prediction on ICSD structures, they achieved a test accuracy of \SI{92.2}{\percent}.
Park {\it et al.} reached a test accuracy of roughly 81\% for a CNN, which classifies space groups of simulated single-phase diffractograms \cite{Park2017}.
A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi et al.\cite{Chitturi2021} They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles.
Zhang {\it et al.} introduce a convolutional self-attention neural network trained on simulated patterns to classify crystal types \cite{zhang2024crystallographic}. Their model was tested on 23,073 unary, binary, and ternary inorganic crystal structures sourced from the COD. The study observed a noticeable performance drop when the pre-trained model was applied to real experimental patterns, as opposed to simulated data. However, their recent work \cite{cao2024simxrd} proposes using convolutional peak descriptors that consider the detector's geometry, which significantly reduces the performance gap in their benchmark tests.
The option of training purely on experimental diffractograms unfortunately is unfeasible because of the limited availability of labeled experimental diffractograms, but Salgado {\it et al.} \cite{Salgado2023} showed, that adding a fraction of experimental patterns to a simulated training dataset improves the performance on unseen experimental patterns. They used \SI{50}{\percent} of the experimental patterns contained in the RRUFF database and added those to their large simulated training set. Then they tested their model's performance on the other half of the RRUFF database and achieved a performance increase in the 230-way spacegroup classification accuracy of \num{11} percentage points compared to the same model only trained on simulated patterns.

@@

The ultimate goal of ML efforts is to make PXRD data identification practical for experimental use, whether for identifying space group symmetry or phase composition. However, the current volume of experimental PXRD patterns is insufficient to effectively train ML models, highlighting an urgent need for a comprehensive experimental PXRD database. To address this, two key approaches are essential. First, developing more sophisticated simulation methods to better approximate experimental patterns\cite{cao2024simxrd}. Second, creating an experimental database that enables transfer learning to bridge the gap between simulated and real-world data. The development of opXRD is particularly significant, as it will provide a comprehensive experimental benchmark for the community, allowing fair comparison of baseline models and accurate evaluation of their applicability in real experimental situations.

### 2024-11-22 chapters/04_our_dataset.tex
Added paragraph by Hodge group

% TODOS:
% - This paper talks about the importance of sharing raw powder X-ray diffraction data. I'd definitely cite it ->  \cite{Aranda2018}

%- The subsections of this section should be the 
% individual contributions that we get from labs

%------------------------------------------$

@@

% Paragraph by Moritz Wolf and Tony-yi 
\subsubsection*{Institute of Catalysis Research and Technology, KIT}

A variety of samples were analyzed including commercial catalysts, bulk reference materials, porous metal oxide particles, and nanoparticles. The latter were synthesized via the surfactant-free benzyl alcohol route. \cite{Wolf2019, Wolf2018} The cobalt oxide (CoO or Co3O4) and cerium oxide (CeO2) nanoparticles were in the size range of 4-16 nm according to the Scherrer equation. A series of porous Al2O3 materials, which were prepared by calcination of boehmite (AlOOH) at various temperatures, represents crystalline samples with limited long-range structure and various contributions of Al2O3 polymorphs.\\

@@

% Paragraph by Bin Cao
\subsubsection*{Guangzhou Municipal Key Laboratory of Materials Informatics, HKUST}

@@

In the past two years, we established a small-scale experimental pXRD database called the X-Ray Phase Identification Public Experimental Dataset (\href{https://github.com/WPEM/XRED}{XRed}). The data in XRed is generated in our lab using instruments such as the Empyrean 3.0, Aeris, and Bruker D8 Advance diffractometers using copper X-ray sources. Hundreds of pXRD patterns have been refined, labeled with CIF files, and organized by elemental systems. The dataset includes original experimental files across single-phase to five-phase mixtures. This project is progressing toward integration with the comprehensive opXRD database to establish a large-scale, long-term experimental resource.

@@

XRD data was measured using a Bruker D8 Discover equipped with a Cu radiation source in a Bragg-Brentano geometry. For the reported data sets the instrument was equipped with a Goebel mirror effectively removing the Cu~K$\beta$ radiation. The data set originates from the combinatorial exploration of the Zn–V–N compositional space, as well as data gathered from multiple research activities on more established metal halide perovskite semiconductors. All data was collected from thin films deposited on borosilicate glass. The Zn–V–N films showed some preferential out-of-plane orientation, while for the perovskites the preferential orientation was minimal, resulting in the presence of all reflections.

@@

We are still in the process of growing the dataset and additional contributions are still very welcome. To find out more about how to contribute to this dataset, visit our website specially designed to collect this dataset, \url{https://xrd.aimat.science} .

>>>>

@@

% Paragraph by Andrea Hodge
\subsubsection*{Department of Chemical Engineering and Materials Science, USC}

Combinatorial CuNi and CuAl samples were synthesized at the University of Southern California (USC) via magnetron co-sputtering from Cu (99.999\%) and Ni (99.995\%) or Al (99.999\%) targets (Plasmaterials) onto stationary 10 cm Si (100) substrates yielding 169 unique 5 x 5mm squares per wafer. These alloys were selected to study compositional effects on stacking fault and growth twin boundary formation in sputtered materials \cite{2024AcMat.27019839A,alwen2024combinatorial}. XRD spectra were collected using a Malvern Panalytical Empyrean X-ray diffractometer at the Forschungszentrum Julich (FZJ) Institute for Energy and Climate Research, Structure and Function of Materials (IEK-2), which enabled automated XRD characterization due to its programmable XY stage and laser sensor for Z height correction. XRD analysis was used to link changes in defect formation in the sputtered films with varied phase and crystal structures. Each composition was characterized using CuK X-rays (1.5406Å wavelength) that were collimated to probe an area of ~4 x 4 mm using a step size of 0.026° and scan duration of 0.3 seconds per step over a 2 range from 30° - 110°. Measurement parameters were chosen to resolve at least six or more points above the full-width half maximum of each XRD peak.

% Paragraph by Moritz Wolf 
\subsubsection*{Institute of Catalysis Research and Technology, KIT}

A variety of samples were analyzed including commercial catalysts, bulk reference materials, porous metal oxide particles, and nanoparticles. The latter were synthesized via the surfactant-free benzyl alcohol route \cite{Wolf2019, Wolf2018}. The cobalt oxide (CoO or Co3O4) and cerium oxide (CeO2) nanoparticles were in the size range of 4-16 nm according to the Scherrer equation. A series of porous Al2O3 materials, which were prepared by calcination of boehmite (AlOOH) at various temperatures, represents crystalline samples with limited long-range structure and various contributions of Al2O3 polymorphs.\\

@@

% Paragraph by Bin Cao and Tong-yi Zhang
\subsubsection*{Guangzhou Municipal Key Laboratory of Materials Informatics, HKUST}

@@

In the past two years, we established a small-scale experimental pXRD database called the X-Ray Phase Identification Public Experimental Dataset (XRed). \footnote{XRed can be found on GitHub at \url{https://github.com/WPEM/XRED}.} The data in XRed is generated in our lab using instruments such as the Empyrean 3.0, Aeris, and Bruker D8 Advance diffractometers using copper X-ray sources. Hundreds of pXRD patterns have been refined, labeled with CIF files, and organized by elemental systems. The dataset includes original experimental files across single-phase to five-phase mixtures. This project is progressing toward integration with the comprehensive opXRD database to establish a large-scale, long-term experimental resource.

@@

XRD data was measured using a Bruker D8 Discover equipped with a Cu radiation source in a Bragg-Brentano geometry. For the reported data sets the instrument was equipped with a Goebel mirror effectively removing the Cu~K$\beta$ radiation. The data set originates from the combinatorial exploration of the Zn–V–N compositional space, as well as data gathered from multiple research activities on more established metal halide perovskite semiconductors. All data was collected from thin films deposited on borosilicate glass. The Zn–V–N films showed some preferential out-of-plane orientation, while for the perovskites the preferential orientation was minimal, resulting in the presence of all reflections. \\

@@

We will continue growing the opXRD dataset, thus additional contributors are very welcome to contact us and submit data through the website. To find out more about how to contribute to this dataset, visit our website \footnote{Datasets can be contributed to opXRD under \url{https://xrd.aimat.science}.} specially designed to collect this dataset.

### 2024-11-22 main.tex
Added paragraph by Hodge group

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4,5]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[11, 12]{Maged Abdelsamie}
\author[6]{Gregoire Heymans}
\author[7]{Alexander Wieczorek}
\author[7]{Siarhei Zhuk}
\author[7]{Sebastian Siol}
\author[8]{Moritz Wolf}
\author[9]{François-Xavier Coudert}
\author[9]{Arthur Hardiagon}
\author[10]{Bin Cao}
\author[13]{Ruth Schwaiger}
\author[10]{Tong-yi Zhang}
\author[4]{Carolin M. Sutter-Fella}
\author[3]{Andrea M. Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Advanced Light Source, Berkeley 94720 CA, USA}
\affil[6]{Lawrence Berkeley National Laboratory, Chemical Sciences Division, Berkeley 94720 CA, USA}
\affil[7]{Empa~–~Swiss Federal Laboratories
for Materials Science and Technology, 8600 Dübendorf,
Switzerland}
\affil[8]{Engler-Bunte-Institut \& Institute of Catalysis
Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[9]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[10]{Guangzhou Municipal Key Laboratory of Materials Informatics,  Hong Kong University of
Science and Technology (Guangzhou), Guangzhou 511400, China}
\affil[11]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia}
\affil[12]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, KFUPM, Dhahran 31261, Saudi Arabia}
\affil[13]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany}
\begin{document}

@@

\section{How to contribute and how to use}\label{sec:how_to_use}
\input{chapters/05_how_to_use}

>>>>

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4,5]{Tim Kodalle}
\author[6]{Hanlin Hu}
\author[7]{Gregoire Heymans}
\author[8]{Alexander Wieczorek}
\author[10]{Arthur Hardiagon}
\author[11]{Bin Cao}
\author[12, 13]{Maged Abdelsamie}
\author[8]{Siarhei Zhuk}
\author[2]{Ben Breitung}
\author[8]{Sebastian Siol}
\author[9]{Moritz Wolf}
\author[10]{François-Xavier Coudert}
\author[14]{Ruth Schwaiger}
\author[11]{Tong-yi Zhang}
\author[4]{Carolin M. Sutter-Fella}
\author[3]{Andrea M. Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Advanced Light Source, Berkeley 94720 CA, USA}
\affil[6]{Hoffmann Institute of Advanced Materials, Shenzhen Polytechnic, Shenzhen 518055, China}
\affil[7]{Lawrence Berkeley National Laboratory, Chemical Sciences Division, Berkeley 94720 CA, USA}
\affil[8]{Empa~–~Swiss Federal Laboratories
for Materials Science and Technology, 8600 Dübendorf,
Switzerland}
\affil[9]{Engler-Bunte-Institut \& Institute of Catalysis
Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[10]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[11]{Guangzhou Municipal Key Laboratory of Materials Informatics,  Hong Kong University of
Science and Technology (Guangzhou), Guangzhou 511400, China}
\affil[12]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia}
\affil[13]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, KFUPM, Dhahran 31261, Saudi Arabia}
\affil[14]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany}
\begin{document}

@@

\section{Summary and Outlook}\label{sec:how_to_use}
\input{chapters/05_how_to_use}
